Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-12 paper/latex/paper.tex
Redo commit 'Add info about TinySOL'

\subsection{Sources}
We used the TinySOL database to create our input data. This database contains samples of notes played using the ordinario style and with three different dynamics for each pair of instrument and pitch : \textit{pp}, \textit{mf} and \textit{ff}. The exact list of samples is shown in Tab.\ref{tab_pitch}.  \textbf{(Should we talk more about TinySOL here?)}

>>>>

\subsection{Sources}
We used the TinySOL database to create our input data. TinySOL is a subset of the Studio On Line (SOL) database created by IRCAM \textbf{Reference needed}. TinySOL contains 1,529 samples from 12 instruments. The instruments come from different orchestral families: strings, woodwinds, and brass. Notes are played using the ordinario style and with three different dynamics for each pair of instrument and pitch : \textit{pp}, \textit{mf} and \textit{ff}. The exact list of samples is shown in Tab.\ref{tab_pitch}.
